### 2017-10-13 Gruba/05-gm.tex

	\stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$. The number of times the $b$ be retweeted, be commented, be liked and the length of the microblog contents are considered. What's more, we also considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}. The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_{f,u}$ in formula \ref{eq:inte}). Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:sim-tw1}.

	\stab(3) \stitle{Interaction Info} includes seven correlation metrics. They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%\end{itemize}

In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem. The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently. As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par

>>>>

%	\stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$. The number of times the $b$ be retweeted, be %commented, be liked and the length of the microblog contents are considered. What's more, we also considers the correlation between %microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}. The correlation metric $C_h$ is in %the form of a normalized vector with each dimension represents one event (similar as $P_{f,u}$ in formula \ref{eq:inte}). Each event %could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:sim-tw1}.

\stab(2) \stitle{Microblog Info} refers to metrics related to the microblog $b$.
%The number of times the $b$ has been retweeted, commented, liked and the length of the microblog contents are considered.
The number that $b$ has been retweeted, commented, liked and the length of $b.M$ (microblog message) are considered.
What's more, we consider the correlation between $b$ and recent event, where the latter is expressed as several core words returned by Ring \cite{IEEEexample:ring}.
Here we compute \textit{TF-IDF weight} $W_f$ of $b.M$, and get correlation metric $C_h$ of $b$ and event by formula \ref{eq:sim-tf1}.

%	\stab(3) \stitle{Interaction Info} includes seven correlation metrics. They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, %microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus %$u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, %and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%\end{itemize}
	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$. 
%In addition, the correlation between microblog contents and $u$'s short-term interest mined from $u$'s recent microblogs (e.g., within 30 days) is also taken in consideration.
%In addition, the correlation between microblog contents and $u$'s short-term interest is also taken in consideration. The short-term %interest is expressed as
In addition, we consider $u$'s short-term interest, which is mined from $u$'s recent microblogs (e.g., within 30 days) and calculated by \textit{TF-IDF}, namely $W_s$. 
The correlation between microblog and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
%%

In this paper, we view modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem.
The advantage of classification model lies in that it could integrate different features conveniently.
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par
